Classical Mechanics Assignment 3

### 2015-10-16 classical/latex/a3.tex
new stuff

@@

\begin{align*}
  \vec{F} &= \sin(\Theta)mg - kmv^2\\
  m\dot{v} &= \sin(\Theta)mg - kmv^2\\
  \frac{dv}{dt} &= \sin(\Theta)g - kv^2\\
  \frac{dv}{\sin(\Theta)g - kv^2} &= dt\\
  \int_0^{v} \frac{dv}{\sin(\Theta)g - kv^2} &= \int_0^t dt\\
  \int_0^{v} \frac{\csc(\Theta)}{g(1 - \frac{\csc(\Theta)k}{g}v^2)}dv &= \int_0^t dt\\
  \frac{\csc(\Theta)}{g}\int_0^{v} \frac{1}{1 - \frac{\csc(\Theta)k}{g}v^2}dv &= \int_0^t dt\\
  \frac{\csc(\Theta)}{g}\int_0^{v} \frac{1}{1 - \frac{\csc(\Theta)k}{g}v^2}dv &= \int_0^t dt
  \hspace{1in} u = \mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}\\
  -\frac{\csc(\Theta)}{g}\mathrm{i}\sqrt{\frac{g}{\csc(\Theta)k}}\int_0^{\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}} \frac{1}{1 + u^2}du &= \int_0^t dt
  \hspace{1in} dv = -\mathrm{i}\sqrt{\frac{g}{\csc(\Theta)k}}du\\
  -\mathrm{i}\frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \int_0^{\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}} \frac{1}{1 + u^2}du &= \int_0^t dt\\
  -\mathrm{i}\frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \tan^{-1}\Bigg(\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= \int_0^t dt\\
  \frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= t\\
  \frac{\tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg)}{\sqrt{kg\sin(\Theta)}} &= t\\ 
\end{align*}

Now we try this...

\begin{align*}
  \frac{\tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg)}{\sqrt{kg\sin(\Theta)}} &= t\\
  \tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= t\sqrt{kg\sin(\Theta)}\\
  v\sqrt{\frac{\csc(\Theta)k}{g}} &= \tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)\\
  v &= \frac{\tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)}{\sqrt{\frac{\csc(\Theta)k}{g}}}\\    
\end{align*}

Now we try integrating...

\begin{align*}
  d &= \int_0^t v(t) dt\\
  d &= \int_0^t \frac{\tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)}{\sqrt{\frac{\csc(\Theta)k}{g}}} dt\\
  d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{\sqrt{\frac{\csc(\Theta)k}{g}}}\\
  d\sqrt{\frac{\csc(\Theta)k}{g}} &= \log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))\\
  e^{d\sqrt{\frac{\csc(\Theta)k}{g}}} &= \cosh\Big(t\sqrt{kg\sin(\Theta)}\Big)\\
  \cosh^{-1}\Bigg(e^{d\sqrt{\frac{\csc(\Theta)k}{g}}}) &= t\sqrt{kg\sin(\Theta)}\\
  \frac{\cosh^{-1}\Big(e^{d\sqrt{\frac{\csc(\Theta)k}{g}}}\Big)}{\sqrt{kg\sin(\Theta)}} &= t\\        
\end{align*}

>>>>

\allowdisplaybreaks

@@

\begin{align*}
  \vec{F} &= \sin(\Theta)mg - kmv^2\\
  m\dot{v} &= \sin(\Theta)mg - kmv^2\\
  \frac{dv}{dt} &= \sin(\Theta)g - kv^2\\
  \frac{dv}{\sin(\Theta)g - kv^2} &= dt\\
  \int_0^{v} \frac{dv}{\sin(\Theta)g - kv^2} &= \int_0^t dt\\
  \int_0^{v} \frac{\csc(\Theta)}{g(1 - \frac{\csc(\Theta)k}{g}v^2)}dv &= \int_0^t dt\\
  \frac{\csc(\Theta)}{g}\int_0^{v} \frac{1}{1 - \frac{\csc(\Theta)k}{g}v^2}dv &= \int_0^t dt\\
  \frac{\csc(\Theta)}{g}\int_0^{v} \frac{1}{1 - \frac{\csc(\Theta)k}{g}v^2}dv &= \int_0^t dt
  \hspace{1in} u = \mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}\\
  -\frac{\csc(\Theta)}{g}\mathrm{i}\sqrt{\frac{g}{\csc(\Theta)k}}\int_0^{\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}} \frac{1}{1 + u^2}du &= \int_0^t dt
  \hspace{1in} dv = -\mathrm{i}\sqrt{\frac{g}{\csc(\Theta)k}}du\\
  -\mathrm{i}\frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \int_0^{\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}} \frac{1}{1 + u^2}du &= \int_0^t dt\\
  -\mathrm{i}\frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \tan^{-1}\Bigg(\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= \int_0^t dt\\
  \frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= t\\
  \frac{\tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg)}{\sqrt{kg\sin(\Theta)}} &= t\\ 
  \frac{\tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg)}{\sqrt{kg\sin(\Theta)}} &= t\\
  \tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= t\sqrt{kg\sin(\Theta)}\\
  v\sqrt{\frac{\csc(\Theta)k}{g}} &= \tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)\\
  v &= \frac{\tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)}{\sqrt{\frac{\csc(\Theta)k}{g}}}\\    
\end{align*}

Now we try integrating out the v:

\begin{align*}
  d &= \int_0^t v(t) dt\\
  d &= \int_0^t \frac{\tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)}{\sqrt{\frac{\csc(\Theta)k}{g}}} dt\\
  d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{\sqrt{kg\sin(\Theta)}\sqrt{\frac{\csc(\Theta)k}{g}}}\\
  d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{\sqrt{\frac{kg}{\csc(\Theta)}}\sqrt{\frac{\csc(\Theta)k}{g}}}\\
 d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{k}\\    
  kd &= \log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))\\
  e^{kd} &= \cosh\Big(t\sqrt{kg\sin(\Theta)}\Big)\\
  \cosh^{-1}(e^{kd}) &= t\sqrt{kg\sin(\Theta)}\\
  \frac{\cosh^{-1}(e^{kd})}{\sqrt{kg\sin(\Theta)}} &= t\\        
\end{align*}
